Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

>>>>

We conclude that $\J_2$ (the set of type-2 result tuples $(r_1, ..., r_{k-2}, h, v)$ where $r_{k-2}$ covers the left endpoint of $h$) can be computed in $F_{k-1}(n, \out) + O(n \log n +  k \cdot \out)$ time. Remember that, to generate the entire type-2 result, we need to repeat the algorithm $4(k-2)$ times (one for each sub-type). The total running time is therefore $O(k) \cdot (F_{k-1}(n, \out) + O(n \log n +  k \cdot \out))$, as claimed in Lemma~\ref{lmm:hv}.
